---
title: "Bootstrapping Samples"
output: html_document
---

Although there are functions in R that allow us to create bootstrapped samples and confidence intervals, it is also relatively straightforward to perform bootstrapping using user-defined functions and loops.  

Say we have a sample from a true underlying distribution

```{r}
set.seed(1293)
pop <- rgamma(10000, shape=1, scale=2)
samplesize=200
samp <- sample(pop, size=samplesize, replace=T)
```


First we will define how many bootstrapped samples we would like to take:
```{r}
boot = 10000
```

Then we will create an empty vector to store the statistics. Here we will use median to demonstrate the usefulness of bootstrapping for statistics with unknown or non-normal distributions.
```{r}
boot.median <- rep(NA,boot)
```

Then we will repeatedly sample, with replacement, a new set of data from the observed sample, and calculate the statistic for each.
```{r}
for (i in 1:boot){
  boot.i <- sample(samp, samplesize, replace=T)
  boot.median[i] <- median(boot.i)
}
```

We can also calculate the variance and the percentile confidence intervals. Here percentile confidence intervals are useful due to the robustness to the distributional form of the statistic.
```{r}
var(boot.median)

ci <- quantile(boot.median,probs=c(.025,.975))
ci
```

We can plot the bootstrapped distributions of medians and show the confidence intervals we have obtained:
```{r, echo=F}
plot(density(boot.median), main="Distribution of Bootstrapped Sample Median", xlab=NA)
abline(v=median(samp))
abline(v=ci[1], col="red")
abline(v=ci[2], col="red")

legend("topleft", c("Percentile CI", "Original Sample Median") ,col=c("red",  "black"), pch=1)

```

