---
title: "Bootstrapping Samples"
output: html_document
---

Although there are functions in R that allow us to create bootstrapped samples and confidence intervals, it is also relatively straightforward to perform bootstrapping using user-defined functions and loops.  

Say we have a sample from a true underlying distribution

```{r}
set.seed(1293)
pop <- rgamma(10000, shape=1, scale=2)
samplesize=100
samp <- sample(pop, size=samplesize, replace=T)
```


First we will define how many bootstrapped samples we would like to take:
```{r}
boot = 10000
```

Then we will create an empty vector to store the statistics (means)
```{r}
boot.mean <- rep(NA,boot)
```

Then we will sample, with replacement, a new set of data from the observed sample, and calculate the statistic for each.
```{r}
for (i in 1:boot){
  boot.i <- sample(samp, samplesize, replace=T)
  boot.mean[i] <- mean(boot.i)
}
```
Now we can plot the results:
```{r}
hist(boot.mean, main="Distribution of Sample Mean, Bootstrap", xlab=NA)

```

We can also calculate the variance and the percentile confidence intervals
```{r}
var <- var(boot.mean)
var

ci <- quantile(boot.mean,probs=c(.025,.975))
ci
```

We can visualize the difference between the bootstrapped CI and the CI from the usual method:
```{r, echo=F}
plot(density(boot.mean), main="Distribution of Sample Mean", xlab=NA)
abline(v=mean(samp))
abline(v=ci[1], col="red")
abline(v=ci[2], col="red")
abline(v=mean(samp)+(1.96*sd(samp)/sqrt(samplesize)), col="blue")
abline(v=mean(samp)-(1.96*sd(samp)/sqrt(samplesize)), col="blue")

legend("topright", c("Bootstrap", "Normal Assumption") ,col=c("red", "blue"), pch=1)

```

